Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-11 paper/structureScene.tex
write ASS results, update ASS figs

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{gfx/unsupervised_test1.eps}
\caption{ASS: $p@k$ obtained for the MFCC and the time-scattering with log compression}
\label{fig:ASS_1}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{gfx/unsupervised_test2.eps}
\caption{ASS: $p@k$ obtained for the time-scattering with and without log compression (w/o log)}
\label{fig:ASS_1}
\end{center}
\end{figure}

@@

What
\subsection{Object-based \vs early integration}

@@

>>>>

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{gfx/unsupervised_test3.eps}
\caption{ASS: $p@k$ obtained for the MFCC and the time-scattering with log compression}
\label{fig:ASS_1}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{gfx/unsupervised_test2.eps}
\caption{ASS: $p@k$ obtained for the time-scattering with and without log compression (w/o log)}
\label{fig:ASS_2}
\end{center}
\end{figure}

This section present evaluation results for the ASS settings. $p@k$ for different settings are showed in the Figures \ref{fig:ASS_1} and \ref{fig:ASS_2}.

@@

Irrespective of the rank $k$ considered, best result is achieved for the time-scattering with log compression using the \emph{ob-c} approach. Overall, the time scattering with the log compression outperform the MFCCs systematically.

\subsection{Object-based \vs early integration}

For both the MFCCs and the time-scattering, \emph{ob-c} and \emph{ob-w} outperform \emph{ei}, thus confirming the benefits of using an object-based representation to refine the similarity measures between the scenes. However, it is worth noticing that \emph{ob-a} perform equivalently to \emph{ei}, which shows that the discriminant information is not carried by all the centroids. To take advantage of an object-based representation, a selection step has to be run on the representatives of the scenes.

Lastly, we see that while \emph{ob-c} and \emph{ob-w} perform equivalently for the MFCCs, \emph{ob-c} seems to be able to better characterized the classes than \emph{ob-w} for the time scattering. This last observation suggests that weighted a centroid according to the number of frames belonging to it may prove to be a limited solution. Indeed, nothing a priori indicates that the discriminant information between two scenes lays within the majority of their frames. On the contrary, two similar environments  \gl{find examples} may shared a lot of similar sound sources \gl{reformulate}.

@@

Outcomes for time-scattering with and without log compression are showed in Figure~\ref{fig:ASS_2}. It can be seen that the log compression strongly improves the results, specially for the \emph{ob} approaches, which perform lesser than \emph{ei} without the log compression. \gl{une idée du pourquoi ?}
